\documentclass[12pt]{article}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{alltt}
\usepackage{array}	
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{verbatim}
\usepackage{setspace}
\usepackage{listings}
\usepackage{amssymb,amsmath, amsthm}
\usepackage{qtree}
\usepackage{oz}
\usepackage[cc]{titlepic}
\usepackage{fancyvrb}


\title{SOEN 331-U: Introduction to Formal Methods\\for Software Engineering\\
Assignment 1 on Object-Z specification}
\author{Shijun Deng(40084956)\\Saebom Shin(40054234)\\Antonio(********)\\Kimchheng(********)}
\date{\today}

\begin{document}
\begin{spacing}{1.5}

\maketitle

\newpage

\section{ParkingManagement}

\begin{class}{ParkingManagement}
\also
\upharpoonright (AllocateVehicle, DeallocateVehicle, FindVehicle) \\
\begin{state}
allocate : LicencePlate \pfun ParkingSpot\\
\where
\end{state} \\
\begin{init}
allocate = \emptyset %\{ \}
\end{init} \\
\begin{op}{AllocateVehicleOK}
\Delta (allocate) \\
newVehicle? : LicencePlate\\
newParkingSpot? : ParkingSpot
\ST
newVehicle? \notin dom~allocate\\
newParkingSpot? \notin ran~allocate\\
allocate' = allocate \cup \{ newVehicle? \mapsto newParkingSpot? \}
\end{op}\\
\begin{op}{DeallocateVehicleOK}
\Delta (allocate) \\
which? : LicencePlate\\
\ST
which? \in dom~allocate\\
allocate' = \{ which? \} \ndres allocate
\end{op}\\
\begin{op}{FindVehicleOK}
\Xi (ParkingManagement)\\
whichToFind? : LicencePlate\\
location! : ParkingSpot
\ST
whichToFind? \in dom~allocate\\
location! = allocate\{ whichToFind? \}
\end{op}\\
...\\
\end{class}

\newpage

\begin{class}{ParkingManagement}
\also
... \\
\begin{op}{VehicleNotFound}
vehicle? : LicencePlate\\
response! : Message
\ST
vehicle? \notin dom~allocate\\
response! =\: 'vehicle \: unknown'
\end{op}\\
\begin{op}{VehicleExists}
vehicle? : LicencePlate\\
response! : Message
\ST
vehicle? \in dom~allocate\\
response! =\: 'Vehicle \: already \: exists'
\end{op}\\
\begin{op}{SpotUnavailable}
newParkingSpot? : ParkingSpot\\
response! : Message
\ST
newParkingSpot? \in ran~allocate\\
response! =\: 'parkingspot \: unavailable'\\
\end{op}\\
~\\
AllocateVehicle \, \hat{=} \, AllocateVehicleOK \,\vee VehicleExists \,\vee SpotUnavailable\\
~\\
DeallocateVehicle \, \hat{=} \, DeallocateVehicleOK \,\vee VehicleNotFound\\
~\\
FindVehicle  \, \hat{=} \, FindVehicleOK \,\vee VehicleNotFound\\
\end{class}


\newpage

\section{ParkingManagement2}

\begin{class}{ParkingManagement2}
\also
\upharpoonright (AllocateVehicle, DeallocateVehicle, FindVehicle) \\
\upharpoonright (GetNumberOfVehicles, ReallocateVehicle, GetAllVehicles) \\
ParkingManagement\\
\begin{state}
counter : \mathbb{N}\\
\where
\end{state} \\
\begin{init}
counter = 0\\
\end{init} \\
\begin{op}{AllocateVehicle}
\ST
counter' = counter + 1 \\
\end{op}\\
\begin{op}{DeallocateVehicle}
\ST
counter' = counter - 1 \\
\end{op}\\
\begin{op}{GetNumberOfVehicles}
\Xi (ParkingManagement2)\\
numberOfVehicles! : \mathbb{N}\\
\ST
numberOfVehicles! = counter\\
\end{op}\\
\begin{op}{ReallocateVehicleOK}
\Delta (allocate) \\
whichVehicle? : LicencePlate\\
moveToWhere? : ParkingSpot
\ST
whichVehicle? \in dom~allocate\\
moveToWhere? \notin ran~allocate\\
moveToWhere? \neq allocate\{ whichVehicle? \} \\
allocate' = allocate \oplus \{ whichVehicle? \mapsto moveToWhere? \}
\end{op}\\
\begin{op}{GetAllVehicles}
\Xi (ParkingManagement2)\\
vehicles! : LicencePlate\\
\ST
vehicles! = dom \: allocate\\
\end{op}\\
\end{class}

\newpage

\begin{class}{ParkingManagement2}
\also
... \\
\begin{op}{SameSpot}
whichVehicle? : LicencePlate\\
moveToWhere? : ParkingSpot\\
response! : Message\\
\ST
moveToWhere? =allocate\{whichVehicle?\}\\
response! =\: 'the \: same \: parkingspot \: as \: the \: current \: one'\\
\end{op}\\
~\\
ReallocateErrors \, \hat{=} \, VehicleExists \,\vee SpotUnavailable \,\vee SameSpot\\
~\\
ReallocateVehicle \, \hat{=} \, ReallocateVehicleOK \,\vee ReallocateErrors\\
\end{class}


\end{spacing}
\end{document}